Association between Breast Cancer and Hepatitis C Virus with Age Controlling

### 2022-12-06 manuscript/manuscript.tex
refs

The rest of the paper is organized into several sections. Section~\ref{sec:data}
describes the study done in 2020 to test if HCV seropositivity is associated with 
breast cancer diagnosis in Egyptian population. Section~\ref{sec:methods} 
describes the following statistical methods; Fisher's Exact Test, Breslow-Day test,
and Mantel-Haenszel method. Section~\ref{sec:app} applies the methods to data 
from the study, including stratafied between ages. Section~\ref{sec:discuss} 
concludes the paper.

@@

\section{Discussion}
\label{sec:discuss}
  Based on the analysis, it is evident that for women under the age of 45,
seropositivity and breast cancer are strongly associated. As being HCV 
positive can complicate treatment of cancer, this is critical information.
In Egypt, breast cancer remains the most common form or cancer and high 
levels of hepatitus C continue.

>>>>

The rest of the paper is organized into several sections that will explain the 
research question and the methods used to evaluate the data. Section~\ref{sec:data}
describes the study done in 2020 to test if HCV seropositivity is associated with 
breast cancer diagnosis in Egyptian population. Section~\ref{sec:methods} 
describes the following statistical methods; Fisher's Exact Test, Breslow-Day test,
and Mantel-Haenszel method, and their respective assumptions. 
Section~\ref{sec:app} applies the methods to data 
from the study, including both crude and stratafied between ages. 
Section~\ref{sec:discuss} concludes the paper with results.

@@

\section{Discussion}
\label{sec:discuss}
  Based on the analysis, it is evident that for women under the age of 45,
seropositivity and breast cancer are strongly associated. However, there 
is not enough to suggest an association for women 45 years and older. 
As being HCV positive can complicate treatment of cancer or act as 
an effective risk factor for increase screening for women, this is 
critical information. More research is necessary to determine how strong 
the association is or further break down age groups into smaller strata.
